---
header-includes:
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \fancyfoot[CO,CE]{For internal use only. Do not share analysis with students.}

output: pdf_document
---

# Pastoral Summary for `r REPORTING_PERIOD`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tufte)
# invalidate cache when the tufte version changes
#knitr::opts_chunk$set(tidy = FALSE,  cache.extra = packageVersion('tufte'))
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

options(htmltools.dir.version = FALSE)
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(ggthemes)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(tidyr)))

# getting data
# should already have effort.data and all.effort.data and mailData from effort_report_script.R
houses <- c("Dobell","Durack","Florey","Mawson","Monash","Oodgeroo")
house_colours <- c("#33CC33","#6600CC","#DDDD00","#0099FF","#CC0000","#FF9900")
house_colours_alt <- c("#338833","#550088","#999900","#0055BB","#880000","#BB5500")

# Tidying data types
all.effort.data$Student.code <- as.factor(all.effort.data$Student.code)
all.effort.data$Category <- factor(all.effort.data$Category, levels = c("Diligence", "Engagement","Behaviour"))
dates <- sort(unique(all.effort.data$Date))
last4dates <- dates[max(1,length(dates)-3):length(dates)]
t1 <- dates[length(dates)]
t0 <- dates[length(dates)-1]

df.means <- all.effort.data %>%
  mutate(Student.name = trim_pref_name(paste(StudentFirstname, StudentSurname))) %>% 
  group_by(Student.code, Student.name, 
           Date, Category, Source, Gender, House, Cohort) %>% 
  summarise(Score = mean(Score))

df.teacher <- df.means[df.means$Source == "Teacher",]
df.teacher <- df.teacher %>% spread(key = Category, value = Score)
df.teacher$Effort <- rowMeans(df.teacher[,c("Diligence","Engagement","Behaviour")])

df.house.summary <- df.teacher[df.teacher$House %in% houses,]

df.cohort.percentiles <- df.house.summary %>% 
  group_by(Cohort, Date) %>% 
  mutate(pr = 100*percent_rank(Effort))
df.cohort.percentiles$pr <- round(df.cohort.percentiles$pr, 1)

df.cohort.percentiles <- df.cohort.percentiles[df.cohort.percentiles$Date >= t0, c("Student.code","Date","pr")] %>% 
  unique()
df.cohort.percentiles <- df.cohort.percentiles %>% spread(key = Date, value = pr)
names(df.cohort.percentiles) <- c("Student.code", "t0", "t1")
df.cohort.percentiles <- df.cohort.percentiles %>% mutate(P.Change = paste0(t0, " to ", t1) )
df.cohort.percentiles$t1 <- NULL
df.cohort.percentiles$t0 <- NULL
```

``` {r}
# Setting up functions for generating house specific reports
topFive <- function(houseSummaryData, date, house = NA, n = 5, top = TRUE) {
  # houseSummaryData as prepared earlier in file - must have the fields:
  # Student.code, Date, Diligence, Engagement, Behaviour, Effort, Student.name, House, Cohort and Gender
  # If top = FALSE then this function returns the bottom n students
  d <- houseSummaryData[houseSummaryData$Date == date,]
  if (!(is.na(house))) {d <- d[d$House == house,]}
  # Cleaning unwanted fields
  d$Date <- NULL
  d$Student.code <- NULL
  # sorting data
  d <- d[order(d$Effort, decreasing = top),]
  d <- d[,c("Student.name","House","Cohort","Gender","Effort")]
  # outputting top n
  n <- min(length(d$Effort),n)
  d <- d[1:n,]
  return(d)
}

effortChange <- function(houseSummaryData) {
  require(knitr)
  dates <- sort(unique(houseSummaryData$Date))
  if (length(dates) < 2) {stop("Less than two dates present: insufficient for change comparison.")}
  t_1 <- dates[length(dates)]
  t_0 <- dates[length(dates)-1]
  d <- houseSummaryData[,c("Student.code","Student.name","Date","House","Cohort","Gender","Effort")]
  d.previous <- d[d$Date == t_0,]
  d.latest <- d[d$Date == t_1,]
  d.previous$Date <- NULL
  d.latest$Date <- NULL
  d.previous$Previous.Effort <- d.previous$Effort
  d.previous$Effort <- NULL
  d.latest$Latest.Effort <- d.latest$Effort
  d.latest$Effort <- NULL
  d <- merge(d.latest, d.previous)
  d$Change <- d$Latest.Effort - d$Previous.Effort
  d <- merge(d, df.cohort.percentiles, all.x = T)
  return(d)
}

bigMovers <- function(houseSummaryData, house = NA, up = TRUE, n = 5) {
  d <- effortChange(houseSummaryData)
  if (!is.na(house)) {d <- d[d$House == house,]}
  d <- d[order(d$Change, decreasing = up),]
  n <- min(length(d$Change), n)
  d$Student.code <- NULL
  return(d[1:n,])
}

CohortToYear <- function(Cohort) {
  require(dplyr)
  # Works with Cohort in the, ahum, 'Cohort':
  # "2018 Year 09"
  # Extracting last 2 digits as number
  Cohort <- as.character(Cohort)
  year <- as.numeric(substr(Cohort, nchar(Cohort)-1, nchar(Cohort)))
  return(year)
}

houseTimelinePlot <- function(houseSummaryData, house, colour1, colour2) {
  require(ggplot2)
  a_lev <- 0.2
  df <- houseSummaryData[houseSummaryData$House == house,] %>% mutate(Year = CohortToYear(Cohort))
  g <- ggplot(df, aes(x = Date, y = Effort, fill = Year, colour = Year, group = Student.code)) 
  g <- g + geom_line(alpha = a_lev) + geom_point(alpha = a_lev)
  g <- g + scale_fill_gradient(low = colour1, high = colour2)
  g <- g + scale_colour_gradient(low = colour1, high = colour2)
  g <- g + scale_y_continuous(limits = c(1,5), labels = c("U","F","G","VG","O"))
  g <- g + ggthemes::theme_tufte()
  g <- g + theme(legend.position = "none") + theme(text = element_text(size = 6))
  return(g)
}
```


## Distribution by house and gender for `r t1`

The 'Effort' score is generated by averaging all subjects in all categories (Diligence, Engagement and Behaviour) for each student. Equal weight is given to each subject.

All effort scores are the teacher reported effort scores unless otherwise noted.

``` {r}
g.hd <- ggplot(data = df.house.summary[df.house.summary$Date == t1,]) + geom_histogram(aes(Effort, fill = House), binwidth = 0.25)
g.hd <- g.hd + scale_fill_manual(values = house_colours) + ggthemes::theme_tufte()
g.hd <- g.hd + scale_x_continuous(limits = c(1,5), labels = c("U","F","G","VG","O"))
g.hd <- g.hd + facet_grid(House ~ Gender)
g.hd <- g.hd + theme(legend.position = "none") + theme(text = element_text(size = 4))
g.hd
```

## House distribution from `r min(last4dates)` to `r t1`

``` {r fig.fullwidth = T, fig.height = 2}
g.ht <- ggplot(data = df.house.summary[df.house.summary$Date %in% last4dates,]) + geom_histogram(aes(Effort, fill = House) ,binwidth = 0.25)
g.ht <- g.ht + scale_fill_manual(values = house_colours) + ggthemes::theme_tufte()
g.ht <- g.ht + scale_x_continuous(limits = c(1,5), labels = c("U","F","G","VG","O"))
g.ht <- g.ht + facet_grid(House ~ Date)
g.ht <- g.ht + theme(legend.position = "none") + theme(text = element_text(size = 4))
g.ht
```

\pagebreak

# Whole school: top, bottom

``` {r}
school_n <- 15
```

## Top `r school_n` 
``` {r}
knitr::kable(topFive(df.house.summary, date = t1, n = school_n), row.names = FALSE, digits = 2)
```

## Bottom `r school_n`
``` {r}
knitr::kable(topFive(df.house.summary, date = t1, n = school_n, top = FALSE), row.names = FALSE, digits = 2)
```

\pagebreak

# Whole school: Biggest movers from `r t0` to `r t1`

## Big movers up
``` {r}
knitr::kable(bigMovers(df.house.summary, up = TRUE, n = school_n), row.names = FALSE, digits = 2)
```

## Big movers down

``` {r}
knitr::kable(bigMovers(df.house.summary, up = FALSE, n = school_n), row.names = FALSE, digits = 2)
```

\pagebreak

# Dobell

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Dobell", colour1 = house_colours[[1]], colour2 = house_colours_alt[[1]])
```

### Top & Bottom 5

``` {r}
t5Dobell <- topFive(df.house.summary, house = "Dobell", date = t1, n = 5)
t5Dobell$House <- NULL
knitr::kable(t5Dobell, row.names = FALSE, digits = 2)
```

``` {r}
b5Dobell <- topFive(df.house.summary, house = "Dobell",date = t1, n = 5, top = FALSE)
b5Dobell$House <- NULL
knitr::kable(b5Dobell, row.names = FALSE, digits = 2)
```

### Big movers

``` {r}
upDobell <- bigMovers(df.house.summary, house = "Dobell", up = TRUE, n = 5)
upDobell$House <- NULL
knitr::kable(upDobell, row.names = FALSE, digits = 2)
```

``` {r}
downDobell <- bigMovers(df.house.summary, house = "Dobell", up = FALSE, n = 5)
downDobell$House <- NULL
knitr::kable(downDobell, row.names = F, digits = 2)
```

\pagebreak

# Durack

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Durack", colour1 = house_colours[[2]], colour2 = house_colours_alt[[2]])
```

### Top & Bottom 5

``` {r}
t5Durack <- topFive(df.house.summary, house = "Durack", date = t1, n = 5)
t5Durack$House <- NULL
knitr::kable(t5Durack, row.names = FALSE, digits = 2)
```

``` {r}
b5Durack <- topFive(df.house.summary, house = "Durack",date = t1, n = 5, top = FALSE)
b5Durack$House <- NULL
knitr::kable(b5Durack, row.names = FALSE, digits = 2)
```

### Big movers

``` {r}
upDurack <- bigMovers(df.house.summary, house = "Durack", up = TRUE, n = 5)
upDurack$House <- NULL
knitr::kable(upDurack, row.names = FALSE, digits = 2)
```

``` {r}
downDurack <- bigMovers(df.house.summary, house = "Durack", up = FALSE, n = 5)
downDurack$House <- NULL
knitr::kable(downDurack, row.names = F, digits = 2)
```

\pagebreak

# Florey

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Florey", colour1 = house_colours[[3]], colour2 = house_colours_alt[[3]])
```

### Top & Bottom 5

``` {r}
t5Florey <- topFive(df.house.summary, house = "Florey", date = t1, n = 5)
t5Florey$House <- NULL
knitr::kable(t5Florey, row.names = FALSE, digits = 2)
```

``` {r}
b5Florey <- topFive(df.house.summary, house = "Florey",date = t1, n = 5, top = FALSE)
b5Florey$House <- NULL
knitr::kable(b5Florey, row.names = FALSE, digits = 2)
```

### Big movers
``` {r}
upFlorey <- bigMovers(df.house.summary, house = "Florey", up = TRUE, n = 5)
upFlorey$House <- NULL
knitr::kable(upFlorey, row.names = FALSE, digits = 2)
```

``` {r}
downFlorey <- bigMovers(df.house.summary, house = "Florey", up = FALSE, n = 5)
downFlorey$House <- NULL
knitr::kable(downFlorey, row.names = F, digits = 2)
```

\pagebreak

# Mawson

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Mawson", colour1 = house_colours[[4]], colour2 = house_colours_alt[[4]])
```

### Top & Bottom 5

``` {r}
t5Mawson <- topFive(df.house.summary, house = "Mawson", date = t1, n = 5)
t5Mawson$House <- NULL
knitr::kable(t5Mawson, row.names = FALSE, digits = 2)
```

``` {r}
b5Mawson <- topFive(df.house.summary, house = "Mawson",date = t1, n = 5, top = FALSE)
b5Mawson$House <- NULL
knitr::kable(b5Mawson, row.names = FALSE, digits = 2)
```

### Big movers
``` {r}
upMawson <- bigMovers(df.house.summary, house = "Mawson", up = TRUE, n = 5)
upMawson$House <- NULL
knitr::kable(upMawson, row.names = FALSE, digits = 2)
```

``` {r}
downMawson <- bigMovers(df.house.summary, house = "Mawson", up = FALSE, n = 5)
downMawson$House <- NULL
knitr::kable(downMawson, row.names = F, digits = 2)
```

\pagebreak

# Monash

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Monash", colour1 = house_colours[[5]], colour2 = house_colours_alt[[5]])
```

### Top & Bottom 5

``` {r}
t5Monash <- topFive(df.house.summary, house = "Monash", date = t1, n = 5)
t5Monash$House <- NULL
knitr::kable(t5Monash, row.names = FALSE, digits = 2)
```

``` {r}
b5Monash <- topFive(df.house.summary, house = "Monash",date = t1, n = 5, top = FALSE)
b5Monash$House <- NULL
knitr::kable(b5Monash, row.names = FALSE, digits = 2)
```

### Big movers

``` {r}
upMonash <- bigMovers(df.house.summary, house = "Monash", up = TRUE, n = 5)
upMonash$House <- NULL
knitr::kable(upMonash, row.names = FALSE, digits = 2)
```

``` {r}
downMonash <- bigMovers(df.house.summary, house = "Monash", up = FALSE, n = 5)
downMonash$House <- NULL
knitr::kable(downMonash, row.names = F, digits = 2)
```


\pagebreak

# Oodgeroo

``` {r fig.height = 2}
houseTimelinePlot(df.house.summary, "Oodgeroo", colour1 = house_colours[[6]], colour2 = house_colours_alt[[6]])
```

### Top & Bottom 5

``` {r}
t5Oo <- topFive(df.house.summary, house = "Oodgeroo", date = t1, n = 5)
t5Oo$House <- NULL
knitr::kable(t5Oo, row.names = FALSE, digits = 2)
```

``` {r}
b5Oo <- topFive(df.house.summary, house = "Oodgeroo",date = t1, n = 5, top = FALSE)
b5Oo$House <- NULL
knitr::kable(b5Oo, row.names = FALSE, digits = 2)
```

### Big movers

``` {r}
upOo <- bigMovers(df.house.summary, house = "Oodgeroo", up = TRUE, n = 5)
upOo$House <- NULL
knitr::kable(upOo, row.names = FALSE, digits = 2)
```

``` {r}
downOo <- bigMovers(df.house.summary, house = "Oodgeroo", up = FALSE, n = 5)
downOo$House <- NULL
knitr::kable(downOo, row.names = F, digits = 2)
```

