---
output: 
  pdf_document:
    latex_engine: xelatex
sansfont: Arial
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# datdir, effort.data needs to be set from script

#source('effort.functions.R') # - needs to be done in script now
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
```


``` {r eval = TRUE}
# This markdown file needs:
#    The data set:          effort.data
#    Student info:          student.info
#    The student id number: ID
# report based on student id number - this will be automated for mail out

df <- effort.data[effort.data$Student.code == ID,]
student.name <- unique(df[df$Student.code == ID,]$Student.name)
cohort <- unique(df[df$Student.code == ID,]$Cohort)
```

``` {r fig.env='marginfigure', fig.height = 1, fig.width = 1}
logo <- png::readPNG("images/oxleycrest.png")
grid::grid.raster(logo)
```

# `r student.name`

## Effort Report - `r reportingPeriod`

Students and teachers reported against the same three categories: _Diligence_, _Engagement_ and _Behaviour_.

* _Diligence_ measures the student's self-discipline, self-reflection, independent motivation, persistence, conscientious application to classwork and homework. 

* _Engagement_ measures their classroom focus, communication (verbal, body language), punctuality, and participation and contribution in groups and class.

* _Behaviour_ measures their classroom conduct and attitude, politeness and respect, and consideration of the learning of others.

The first graph shows the average of the student's self reported scores, and their teachers' scores, across all subjects. The second graph shows the breakdown per subject. The third graph shows the effort progress over time compared to the student's cohort.

&nbsp;

### Effort report for `r student.name`

``` {r fig.height = 4, fig.width = 8, fig.align = "center"}
overallEffortPlot(df)
```

``` {r fig.height = 15, fig.width = 13, fig.align = "center"}
effortPlot(df, ctitle = "Effort by Subject")
```

--------

``` {r fig.height = 4, fig.width = 8, fig.align = "center"}
g.timeline <- suppressWarnings(
  effortIndividualTimeline(all.effort.data,ID, title = paste0("Effort timeline for ",student.name, ", with cohort comparison in grey"), student.info = effort.data)
)
g.timeline
```