---
output: 
  pdf_document:
    latex_engine: xelatex
sansfont: Gill Sans
geometry: margin=1in
---

``` {r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('effort.functions.R')
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
```

``` {r eval = TRUE}
# This markdown file needs:
#    The data set: d
#    The student id number: student.id
#    The student's name: student.name

# importing data for sampel run - comment this out for running from script, or set Eval to FALSE
d <- read.csv('sample.effort.csv')
names(d) <- c("Student.ID", "Teacher.ID", "Subject", "Source", "Category", "Score")
# report based on student id number - this will be automated for mail out
student.id <- 1971
# Get full name based on student.id
student.name <- "Jen Eric"
```

``` {r fig.env='marginfigure', fig.height = 1, fig.width = 1}
logo <- png::readPNG("images/oxleycrest.png")
grid::grid.raster(logo)
```

# `r student.name`

## Effort Report - Term 1 2017

Students and teachers reported against the same three categories: _Diligence_, _Engagement_ and _Behaviour_.

* _Diligence_ measures the student's self-discipline, self-reflection, independent motivation, persistence, conscientious application to classwork and homework. 

* _Engagement_ measures their classroom focus, communication (verbal, body language), punctuality, and participation and contribution in groups and class.

* _Behaviour_ measures their classroom conduct and attitude, politeness and respect, and consideration of the learning of others.

The first graph shows the average of the student's self reported scores, and their teachers' scores, across all subjects. The second page shows the breakdown per subject.

&nbsp;

``` {r fig.height = 4, fig.width = 7}
d <- d[d$Student.ID == student.id,]
overall <- overallEffortPlot(d)
overall
```

\newpage

``` {r fig.height = 7, fig.width = 7}
d <- d[d$Student.ID == student.id,]
breakdown <- effortPlot(d, "Effort by Subject")
breakdown
```
