---
output: html_document
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE,  cache.extra = packageVersion('tufte'))
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(htmltools.dir.version = FALSE)
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(ggthemes)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(tidyr)))

# Getting data 
datdir <- "/Users/benhicks/Documents/Data Analysis/Data-Oxley/Effort Data/2017 Term 1"
df <- read.csv(paste0(paste0(datdir, "/2017 Term 1 Effort Data.csv")))
student.info <- read.csv(paste0(datdir,"/StudentInfo.csv"))

# Processing data for comparisons
df$Category <- factor(df$Category, levels = c("Diligence", "Engagement","Behaviour"))
df <- unique(merge(df, student.info))

classCodes <- unique(df$Class.code)

df.total <- unique(df) %>% spread(Category, Score)
df.total$Effort <- df.total$Diligence + df.total$Engagement + df.total$Behaviour
df.total <- subset(df.total, select = -c(Diligence, Engagement, Behaviour))
df.total <- merge(df.total, student.info)

df.overall <- df.total %>% group_by(Student.name, Subject, Source, Gender) %>% summarise(Effort = mean(Effort))

df.overall <- df.overall %>% group_by(Student.name, Source) %>% summarise(Effort = mean(Effort))

df.total.wide <- df.overall %>% spread(Source, Effort)
df.total.wide <- merge(df.total.wide, student.info)
df.total.wide$Year <- as.factor(df.total.wide$Year)

df.comp <- df %>% spread(Source, Score)
df.comp$Difference <- df.comp$Student - df.comp$Teacher
```

# Effort Analysis

Effort analysis of 7 - 12 effort collected in Term 1 2017. Report generated `r Sys.Date()`

## Distributions by Category

The distribution of all the grades is displayed on the right.

``` {r fig.margin = T, fig.height = 8, fig.fullwidth = F}
g1 <- ggplot(data = df, aes(x = Category, y = Score, color = Source, label = Student.name)) + 
  geom_jitter(alpha = 0.02, width = 0.4) + 
  scale_color_brewer(palette = "Set2")+
  facet_wrap(~Source) + 
  theme_tufte() + 
  theme(axis.text.x = element_text(angle = 90))
g1 + ggtitle("Distribution of effort grades")
```

\hfill

## Student teacher comparison

The following graphs display the difference between the teacher score and the student score. It is calculated by _student - teacher_ so a positive score indicates the student is reporting higher, and a negative score means the teacher is recording higher. 

``` {r fig.margin = F}
df.comp.complete <- df.comp[complete.cases(df.comp),]
gg <- ggplot(df.comp, aes(Difference)) + geom_density(bw = 0.5) + scale_y_continuous(labels = NULL) + scale_x_continuous(limits = c(-3.5,3.5)) +
  theme_tufte() + theme(text = element_text(size = 5))
```

&nbsp;

``` {r fig.margin = F, fig.fullwidth = F, fig.height = 1}
gg + ggtitle("Overall individual score comparison: Student - Teacher")
```

&nbsp;

## Student teacher comparison, by year level

``` {r fig.fullwidth = F, fig.height = 1}
gg +facet_grid(. ~ Year) + ggtitle("Individual score camparison by Year level: Student - Teacher") + 
  theme(text = element_text(size = 5),strip.text.y = element_blank()) + theme(axis.ticks.y = element_blank(), axis.text.y=element_blank(), 
            axis.title.y = element_blank())
```

\newpage

## Category, Source, Subject and Gender analysis

Distribution of total effort score (Diligence + Engagement + Behaviour), with teacher student comparison.

``` {r fig.align = "center", fig.fullwidth = F, fig.margin = F, fig.height = 2}
g2 <- ggplot(df.total.wide, aes(x = Teacher, y = Student, color = Gender, label = Student.name)) + 
  geom_jitter(width = 0.3, height = 0.5, alpha = 0.2, size = 0.8) + 
  coord_fixed(ratio = 1, xlim = c(3,15), ylim = c(3,15)) + 
  theme_tufte() + theme(text = element_text(size = 5))
g2 + ggtitle("Teacher vs Student effort score")
```


&nbsp;

## Total effort score, split by category, gender and source.

The following graphs compare the overall effort distrubution split on gender and source. The overall distribution of these is below and in the margin it is split by category.

``` {r fig.align = "center", fig.margin = T, fig.height = 5}
g3_1 <- ggplot(df, aes(Score, color = Gender, linetype = Source)) +
  geom_density(bw = 0.5) + theme_tufte() + theme(text = element_text(size = 6))
g3_1 + facet_grid(Category ~ Gender) + ggtitle("Gender, Source, Category comparison") + ggtitle("Distribution by category, gender and source")
```

&nbsp;

``` {r fig.margin = F, fig.fullwidth = F, fig.height = 2}
g3 <- ggplot(df.total, aes(Effort, color = Gender, linetype = Source)) + geom_density(bw = 1) + theme_tufte() + theme(text = element_text(size = 5))
g3 + facet_grid(. ~ Gender) + ggtitle("Distribution by gender and source")
```


``` {r eval = FALSE}
# Mucking around with maths data
df.maths <- df[df$Class.code %in% mathsClasses,]
g_m <- ggplot(df.maths, aes(Score, linetype = Source)) +
  geom_density(bw = 0.5) + theme_tufte() + theme(text = element_text(size = 6))
g_m + facet_grid(Category ~ Year) + ggtitle("Year, Source, Category comparison for Mathematics classes")
```



``` {r fig.height = 30, fig.align = "center", eval = FALSE}
# Not evaluating in PDF output
g3 + facet_grid(Subject ~ Gender, scales = "free") + ggtitle("Distribution by gender, source and subject")
```

